TGI Spinal Analysis Code

### 2022-12-07 analysis/tgi-spinal_analysis.Rmd
small changes

# transform variables into proportions (aka divide by 100), this makes the effect size estimates more logical
df_long$beta <- df_long$beta/100
df_long$ID <- factor(df_long$ID)
```
# Cold
# Warm
# Burn

# Run one regression including quality as a predictor
```{r}
# Try and model all with ratings
model.all = glmmTMB::glmmTMB(beta ~ manipulation + condition + cold_cond + quality + trial_n +
                                quality*manipulation*condition + (1|ID),
                      family = glmmTMB::beta_family(),
                      ziformula = ~1+manipulation,
                      data = df_long,
                      na.action = na.omit) 
summary(model.all)
```

>>>>

# transform variables into proportions (aka divide by 100), this makes the effect size estimates more logical
df_long$beta <- df_long$beta/100
df_long$ID <- factor(df_long$ID)
```

# Cold
```{r coldmod}
# Try and model all with ratings
model.cold = glmmTMB::glmmTMB(beta ~ manipulation + condition + cold_cond + trial_n +
                                manipulation*condition*cold_cond + (1|ID),
                      family = glmmTMB::beta_family(),
                      ziformula = ~1+manipulation + (1|ID),
                      data = df_long %>% filter(quality == 'cold'),
                      na.action = na.omit) 
summary(model.cold)
```
# Warm
```{r coldmod}
# Try and model all with ratings
model.warm = glmmTMB::glmmTMB(beta ~ manipulation + condition + cold_cond + trial_n +
                                manipulation*condition*cold_cond + (1|ID),
                      family = glmmTMB::beta_family(),
                      ziformula = ~1+manipulation + (1|ID),
                      data = df_long %>% filter(quality == 'warm'),
                      na.action = na.omit) 
summary(model.warm)
```

# Burn

# Run one regression including quality as a predictor
